### 2024-03-29 doc/sections/mav-semantics.tex
[ tex ] title, grant ack, and small fixes

@@

In the Phase Semantics, structures are interpreted as elements that are
fixed points of a closure operator defined by a double negation with
respect to the monoid on the original frame. This closure operator
generates a partial order of ``facts'' whose meets and joins exactly
correspond to the syntactic ones when the original monoid is derived
from the proofs. As we mentioned in the introduction, the presence of
a self-dual operator in BV means that we cannot use double negation
closure, and we have to proceed more deliberately to preserve
join-like structure in an MAV-frame when building MAV-algebras. We do
this by defining $+$-closed lower sets as those that are closed under
finite $+$-combinations of their elements. This leads to a closure
operator on lower sets that allows us to immediately deduce that
$+$-closed lower sets form a lattice. We also preserve the
Day-pomonoids from lower sets, but in two different ways, depending on
how the original pomonoid interacts with $+$. In \Cref{prop:closed-monoid-distrib} we handle pomonoids that distribute
over $+$, and in \Cref{prop:closed-monoid-duoidal} we
handle pomonoids that are entopic under $+$. We need these
constructions to lift the $\parr$ and $\lhd$ pomonoids from
MAV-frames to $+$-closed lower sets. Finally in this section, we show
that duoidal structure on lower sets from
\Cref{prop:lower-set-duoidal} is preserved in $+$-closed lower sets.

>>>>

\begin{remark}
  More generally, if $P \vInferFrom* Q$ in MAV, then
  $\sem{Q} \leq \sem{P}$ in an MAV-algebra. Note that the ordering is
  reversed! It will be reversed again in the definition of MAV-frame.
\end{remark}

@@

In the Phase Semantics, structures are interpreted as elements that are
fixed points of a closure operator defined by a double negation with
respect to the monoid on the original frame. This closure operator
generates a partial order of ``facts'' whose meets and joins exactly
correspond to the syntactic ones when the original monoid is derived
from the proofs. As we mentioned in the introduction, the presence of
a self-dual operator in BV means that we cannot use double negation
closure, and we have to proceed more deliberately to preserve
join-like structure in an MAV-frame when building MAV-algebras. We do
this by defining $+$-closed lower sets as those that are closed under
finite $+$-combinations of their elements. This leads to a closure
operator on lower sets that allows us to immediately deduce that
$+$-closed lower sets form a lattice. We also preserve the
Day-pomonoids from lower sets, but in two different ways, depending on
how the original pomonoid interacts with $+$. In \Cref{prop:closed-monoid-distrib} we handle pomonoids that distribute
over $+$, and in \Cref{prop:closed-monoid-duoidal} we
handle pomonoids that are duoidal under $+$. We need these
constructions to lift the $\parr$ and $\lhd$ pomonoids from
MAV-frames to $+$-closed lower sets. Finally in this section, we show
that duoidal structure on lower sets from
\Cref{prop:lower-set-duoidal} is preserved in $+$-closed lower sets.
